A coupled particle level set and Moment-of-fluid method for simulating multiphase flows with phase change \thanks{this material is based upon work supported by National Aeronautics and Space Administration under grant number 80NSSC20K0352}

### 2024-03-11 main.tex
working on the intro

Multiphase flow examples are shown in 2D, 3D axisymmetric ``RZ,'' and 
3D coordinate systems.  Examples include two material and three 
material multiphase flows: bubble formation, the impingement of a 
liquid jet on a gas bubble in a cryogenic fuel tank, freezing, melting,
evaporation, and liquid lens dynamics.
%%compare with Vu SI.
% Fred Stern -> reconstructed distance function coupled with VOF 
%%cite: Mukundan
\linenumbers
\section{Introduction}
We present an improved ``Continuous Moment-of-Fluid'' (CMOF) algorithm
for computing solutions to multiphase (multimaterial) flows.  We 
demonstrate the benefits of our new algorithm, beyond that of the 
current state-of-the-art, on these benchmark multiphase flow
problems:
bubble formation\cite{helsby1955behaviour} (see Section \ref{bubform}),
freezing\cite{hu2010icing} (see Section \ref{freezing_sec}), 
liquid lens\cite{MIAO2021109358} (see Section \ref{liqlens}),
and bubble dynamics in a Cryogenic fuel 
tank\cite{bentz1993low} (see Section \ref{TPCEsec}).

>>>>

Multiphase flow examples are shown in 2D, 3D axisymmetric ``RZ,'' and 
3D coordinate systems.  Examples include two material and three 
material multiphase flows: bubble formation, the impingement of a 
liquid jet on a gas bubble in a cryogenic fuel tank, freezing, melting,
evaporation, and liquid lens dynamics.
%%compare with Vu SI.
% Fred Stern -> reconstructed distance function coupled with VOF 
%%cite: Mukundan
\linenumbers
\section{Introduction}
In Ye et al\cite{YeEstebe...},
an improved ``Continuous Moment-of-Fluid'' (CMOF) algorithm
for computing solutions to multiphase (multimaterial) flows was
presented for overcoming the interface curvature ``checkerboard'' problem
present in the ``Moment of Fluid'' (MOF) \cite{MOF}  method.  
Also in Ye et al\cite{YeEstebe...}, a novel decision tree data science 
approach was presented for accelerating the CMOF slope reconstruction 
algorithm.

In this article, we present a ``Particle Level Set Moment-of-Fluid''
method for overcoming the interface checkerboard prolem.  This new approach
we claim is more accurate and faster than the CMOF approach and 
does not require the expensive initial training step.  We also claim that
our new approach is faster and more accurate than the CLSVOF 
method\cite{SusPuckett} with the added capability for simulating
general multimaterial (>2 materials) mutiphase flows.

We 
demonstrate the benefits of our new algorithm, beyond that of the 
current state-of-the-art, on these benchmark multiphase flow
problems:
bubble formation\cite{helsby1955behaviour} (see Section \ref{bubform}),
freezing\cite{hu2010icing} (see Section \ref{freezing_sec}), 
liquid lens\cite{MIAO2021109358} (see Section \ref{liqlens}),
and bubble dynamics in a Cryogenic fuel 
tank\cite{bentz1993low} (see Section \ref{TPCEsec}).
